---
title: "simpleRegress"
author: "Genevieve Metcalf"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

We are comparing the variable neck and the variable chest to see what variable is better at determining length.



## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Neck as a variable for determining a bears length had adjusted r square score of 0.7476.

The scatter plot shows that as neck size goes up, length does as well. Thus neck is a good predictor to determine length of a bear.


## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE,interval = "prediction")
```

## Numerical Summary

```{r}
cor(bears$LENGTH,bears$NECK)
```

The correlation coefficient.


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

Chest as a variable for determining a bears length had adjusted r square score of 0.7869

The scatter plot shows that as chest size goes up, length does as well. Thus chest is a good predictor to determine length of a bear.

## Numerical Summary

```{r}
cor(bears$LENGTH,bears$CHEST)
```

The correlation coefficient.

## Conclusion

Chest had an adjusted r square score of 0.7869 while neck had an adjusted r square score of 0.7476.
Chest is a better predict in length than neck because the adjusted r square of the fit for chest was larger than the adjusted r square for neck. 